Modalities for Location Virtualization

### 2022-09-18 semantics.tex
+

\section{Semantics}
\label{sec:semantics}
\subsection{Instructions}
\label{sec:instrsemantics}
The syntax of instructions is given in \fref{fig:syntax}. Their
small-step operational semantics, a~reduction relation of the form
$\hsfork{\instr}{\store}{\instr'}{\store'}{\instrs}$,
is defined in \fref{fig:semantics}.
%
The last argument~$\instrs$ is a list of newly-spawned threads;
when it is empty, we omit it
and write just $\hs{\instr}{\store}{\instr'}{\store'}$.
%
% Also, when it is a singleton, we omit the square brackets (StepFork).

% We briefly review the syntax and reduction rules.
%
The no-op ``$\iskip$'' and the sequencing construct
``$\iseq{\instr_1}{\instr_2}$'' are standard.
%

>>>>

\section{Semantics}
\label{sec:semantics}
\subsection{State}
\label{sec:state}
We represent the machine state mainly as a finite map of registers to register values and a map of masked physical memory addresses to 64-bit physical memory values. Together with default def\textsf{CPU} instantiation, we end up having our state with following pieces:
\begin{itemize}
\item A constant cpu initialized with default value: $\sigma.\mathcal{C}$
\item A register map: $\sigma.\mathcal{R}: \kw{greg} \rightarrow_{\textrm{fin}} \kw{regval} $
\item A memory map: $\sigma.\mathcal{M}: \Loc \rightharpoonup_{\textrm{fin}} (\rightharpoonup_{\textrm{fin}} )$
\end{itemize}

\subsection{Indexed Memory \& Register References}
\label{sec:}
As one might have already anticipated from the syntax we introduce, we do not bind any value of an evaluated expression. All the indices and accessed values are treated as globally referenced. In align with this design choice, our expression is a stream of instructions, which is not evaluated to a value to be bound, but changes the machine state through the indices (e.g. $\kw{r}\in\kw{greg}$) -- to the global maps. 
\subsection{Instructions}
\label{sec:instrsemantics}
The syntax of instructions is given in \fref{fig:syntax}. Their
small-step operational semantics, a~reduction relation of the form
$\hsfork{\instr}{\store}{\instr'}{\store'}{\instrs}$,
is defined in \fref{fig:semantics}.
%
The last argument~$\instrs$ is a list of newly-spawned threads;
when it is empty, we omit it
and write just $\hs{\instr}{\store}{\instr'}{\store'}$.
%
% Also, when it is a singleton, we omit the square brackets (StepFork).

% We briefly review the syntax and reduction rules.
%

### 2022-09-18 syntax.tex
+

\section{Syntax}
\label{sec:syntax}
\subsection{Registers, Memory Indices}
There exist two pieces of resources we access in our model: registers and memory. A register identifier, $\reg$, is chosen from a fixed finite set of register identifiers,$\regset$. We use these identifiers to access the register values, $\regval \in \regvaltype$. Unlike registers, we do not abstract the memory indices as a special type but instead, for the sake of clarity and ease of representation, we show differently masked machine words, $\loc \in \Loc$, with the subscripts showing the length of a 64-bit machine word after masking, e.g. $\kw{w}_{12}$ is a 12-bit resource which can be obtained after masking 52-bit of a 64-bit word.
This simple syntax in \ref{fig:syntax} includes a simple syntax for values because our language is purely \textit{imperative}, i.e. an instruction does not return a value. Intentionally, we restrict any stream of instruction, $\instrs$, to eventually reduce to $\iskip$ instruction which is injected into unit.
\input{fig-syntax}
\subsection{State}
\label{state}

>>>>

\section{Syntax}
\label{sec:syntax}
\subsection{Registers, Memory Indices}
Programs we demonstrate in this paper requires accessing two types of computer resource: registers and memory. A register identifier, $\reg$, is chosen from a fixed finite set of register identifiers,$\regset$. We use these identifiers to access the register values, $\regval \in \regvaltype$. Unlike registers, we do not abstract the memory indices as a special type but instead, for the sake of clarity and ease of representation, we show differently masked machine words, $\loc \in \Loc$, with the subscripts showing the length of a 64-bit machine word after masking, e.g. $\kw{w}_{12}$ is a 12-bit resource which can be obtained after masking 52-bit of a 64-bit word.
This simple syntax in \ref{fig:syntax} includes a simple syntax for values because our language is purely \textit{imperative}, i.e. an instruction does not return a value. Intentionally, we restrict any stream of instruction, $\instrs$, to eventually reduce to $\iskip$ instruction which is injected into unit. Our syntax capture the no-op ``$\iskip$'' and the sequencing construct ``$\iseq{\instr}{\instrs}$'' in their standard forms.
\input{fig-syntax}
\subsection{State}
\label{state}
